Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-04 thesis/paper.tex
Intro to disc

\newpage
\section{Discussion}
Our results have been valuable in exploring the motives behind API changes and the causes of API evolution. When Analysing these results, the following interesting topics came to light:

Intro with a generic motivation for the study e.g. ``the results and insight into the API development suggest the following things'':

``The results of our study allow us to formulate the following implications of our study:''

\newpage
\subsection{Discussion RQ1}

@@

\newpage
\subsection{Discussion RQ1.1}

@@

\newpage
\subsection{Discussion RQ2}

@@

\newpage

>>>>

\section{Discussion}
Our results have been provided valuable insight to the motives behind the evolution of an API. The results show that APIs definitely can be studied from the point of view of old evolution theories. Based on the result, we have formulated the subsequent outcomes.

\subsection{Discussion RQ1}

@@

\subsection{Discussion RQ1.1}

@@

\subsection{Discussion RQ2}

@@
